{\itshape Advanced Robotics} A simple path optimization method for motion planning

### 2015-10-16 paper.tex
Remove cost column, fix typo

@@

We iterate step~(\ref{eq:iteration-1}) until path $\xx_{i+1}$ is in collision. 
When a collision is detected, we introduce a constraint and perform a new 
iteration from $\xx_i$ as explained in the next section. We use a continuous 
collision checker inspired of~\cite{SchwarzerExactCollision} to validate our 
paths and to return the first colliding configuration along a path. This step corresponds to \texttt{validatePath} in Algorithm~\ref{algo:gradient}.

@@

Let $M^{*}\in SE(3)$ denote the homogeneous transformation between frames of $
\body_1$  and $\body_2$ in configuration 
$\x_i(\tcolli)$. Let $M\in SE(3)$ denote the same transformation in configuration 
$\x (\tcolli)$ where $\x$ is any path 
in $\CS^{wp}$. Let $R\in SO(3)$ and $\translation\in\real^3$ 
(resp. $\translation^{*}$) be the rotation 
and translation parts of $M$ (resp. $M^{*}$).

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.0cm,height=6.8cm]{pr2_orth_constr_results.png}
	\includegraphics[width=7.0cm,height=6.8cm]{ur2_orth_constr_results.png}\\
	\vspace{0.05cm}
	\includegraphics[width=7.0cm,height=6.3cm]{ur5sph_orth_constr_results.png}
	\includegraphics[width=7.0cm,height=6.3cm]{puzzle_orth_constr_results.png}
	\caption{Trajectories of wrists, end-effectors or center allong different paths: the initial path is represented in red, the RS optimized path in blue and the GB optimized path ($\alpha_{init}=0.1$) in green. For the freeflyer puzzle (bottom right), points $\po_1$, $\po_2$ and vectors $\mathbf{u}$ for constraints computation are also shown in grey and red.}
	\label{trajectories}
\end{figure}

@@

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{cccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Cost & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $14.3$ & $ $ &\\
    \textbf{Freeflyer-} & GB & $\,\text{ms}$ & $ $ & $ $ &\\
    \textbf{puzzle} & PRS & $6.53\,\text{ms}$ & $14.3$ & $ $ &\\
    & RS & $68.3\,\text{ms}$ & $6.05$ & $ $ &\\
    \midrule
    & Initial &  & $11.3$ & $ $ &\\
    \textbf{Double-arm} & GB & $318\,\text{ms}$ & $4.95$ & $ $ &\\
    \textbf{5-DOF} & PRS & $8.42\,\text{ms}$ & $8.73$ & $ $ &\\
    & RS & $61.9\,\text{ms}$ & $6.96$ & $ $ &\\
    \midrule
    & Initial &  & $10.8$ & $ $ & $8.03$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $24.8\,\text{s}$ & $1.90$ & $ $ & $10^{-7}\,\text{m}$\\
    \textbf{arms} & PRS & $41.1\,\text{s}$ & $ 4.73$ & $ $ & $0\,\text{m}$\\
    & RS & $31.5\,\text{s}$ & $1.60$ & $ $ & $2.70\,\text{m}$\\
    \midrule
    & Initial &  & $15.0$ & $ $ &\\
    \textbf{PR2-in-} & GB & $288\,\text{s}$ & $4.40$ & $ $ &\\
    \textbf{kitchen} & PRS & $431\,\text{s}$ & $12.1$ & $ $ &\\
    & RS & $95.6\,\text{s}$ & $5.33$ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{with-spheres} & PRS & $\,\text{s}$ & $ $ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $ $ & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ & $ $ &\\
    \textbf{through-window} & PRS & $\,\text{s}$ & $  $ & $ $ &\\
    & RS &  $\,\text{s}$ & $ $ & $ $ &\\
    \midrule
    & Initial &  & $19.0$ & $ $ &\\
    \textbf{Baxter-in-} & GB & $2449\,\text{s}$ & $5.85$ & $ $ &\\
    \textbf{office} & PRS & $638\,\text{s}$ & $17.5$ & $ $ &\\
    & RS & $139\,\text{s}$ & $13.3$ & $ $ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM as initial 
guess for each optimizer. $\alpha_{init}$ is set to 0.1.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}

>>>>

????? This paper is based on a similar work, which has been sent to ICRA, with a different type of collision constraints.

@@

We iterate step~(\ref{eq:iteration-1}) until path $\xx_{i+1}$ is in collision. This 
corresponds to the unconstrained function \texttt{computeIterate} in 
Algorithm~\ref{algo:gradient}.
When a collision is detected, we introduce a constraint and perform a new 
iteration from $\xx_i$ as explained in the next section. We use a continuous 
collision checker inspired of~\cite{SchwarzerExactCollision} to validate our 
paths and to return the first colliding configuration along a path. This step corresponds to \texttt{validatePath} in Algorithm~\ref{algo:gradient}.

@@

Let $M^{*}\in SE(3)$ denote the homogeneous transformation between frames of $
\body_1$  and $\body_2$ in configuration 
$\xx_i(\tcolli)$. Let $M\in SE(3)$ denote the same transformation in configuration 
$\xx (\tcolli)$ where $\xx$ is any path 
in $\CS^{wp}$. Let $R\in SO(3)$ and $\translation\in\real^3$ 
(resp. $\translation^{*}$) be the rotation 
and translation parts of $M$ (resp. $M^{*}$).

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=7.0cm,height=6.8cm]{pr2_orth_constr_results.png}
	\includegraphics[width=7.0cm,height=6.8cm]{ur2_orth_constr_results.png}\\
	\vspace{0.05cm}
	\includegraphics[width=7.0cm,height=6.3cm]{ur5sph_orth_constr_results.png}
	\includegraphics[width=7.0cm,height=6.3cm]{puzzle_orth_constr_results.png}
	\caption{Trajectories of wrists, end-effectors or center allong different paths: the initial path is represented in red, the RS optimized path in blue and the GB optimized path ($\alpha_{init}=0.1$) in green.}
	\label{trajectories}
\end{figure}

@@

\begin{table}
\centering
\scalebox{0.9}{
  \begin{tabular}{ccccc}
  \toprule
    \textbf{Problem} & Path obtained from & Computation time  & Path length & Base traveled distance\\
    \midrule
    \midrule
    & Initial &  & $14.3$  &\\
    \textbf{Freeflyer-} & GB & $\,\text{ms}$ & $ $  &\\
    \textbf{puzzle} & PRS & $6.53\,\text{ms}$ & $14.3$  &\\
    & RS & $68.3\,\text{ms}$ & $6.05$  &\\
    \midrule
    & Initial &  & $11.3$  &\\
    \textbf{Double-arm} & GB & $318\,\text{ms}$ & $4.95$  &\\
    \textbf{5-DOF} & PRS & $8.42\,\text{ms}$ & $8.73$  &\\
    & RS & $61.9\,\text{ms}$ & $6.96$  &\\
    \midrule
    & Initial &  & $10.8$  & $8.03$\,\text{m}\\
    \textbf{PR2-crossing-} & GB & $24.8\,\text{s}$ & $1.90$  & $0\,\text{m}$\\
    \textbf{arms} & PRS & $41.1\,\text{s}$ & $ 4.73$ & $0\,\text{m}$\\
    & RS & $31.5\,\text{s}$ & $1.60$ & $2.70\,\text{m}$\\
    \midrule
    & Initial &  & $15.0$ &\\
    \textbf{PR2-in-} & GB & $288\,\text{s}$ & $4.40$ &\\
    \textbf{kitchen} & PRS & $431\,\text{s}$ & $12.1$ &\\
    & RS & $95.6\,\text{s}$ & $5.33$ &\\
    \midrule
    & Initial &  & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ &\\
    \textbf{with-spheres} & PRS & $\,\text{s}$ & $ $ &\\
    & RS & $\,\text{s}$ & $ $ &\\
    \midrule
    & Initial &  & $ $ &\\
    \textbf{6-DOF-arm-} & GB & $\,\text{s}$ & $ $ &\\
    \textbf{through-window} & PRS & $\,\text{s}$ & $  $ &\\
    & RS &  $\,\text{s}$ & $ $ &\\
    \midrule
    & Initial &  & $19.0$ &\\
    \textbf{Baxter-in-} & GB & $2449\,\text{s}$ & $5.85$ &\\
    \textbf{office} & PRS & $638\,\text{s}$ & $17.5$ &\\
    & RS & $139\,\text{s}$ & $13.3$ &\\
    \bottomrule
  \end{tabular}
  }%scalebox
\caption{Average results for 30 runs of several examples presented in the paper or 
the video. For each run, a solution path is planned by Visibility-PRM as initial 
guess for each optimizer. $\alpha_{init}$ is set to 0.1.
For the PR2-crossing-arms example only, the right column represents the 
distance that is traveled by the robot mobile base during the different paths.
}
\label{tab:results}
\end{table}
